Effective Reionization Likelihood from Planck 2018 Data (?)

### 2021-02-13 paper/rei.tex

\begin{figure}[t]
\includegraphics[width=0.47\textwidth]{results/cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri.png}
\caption{Marginalized posteriors for $\tauhi$ and $\taulo$ in the two-step model described in \refssec{example2}: effective reionization likelihood with f = 0.14 (red) agrees very well with the full likelihood results (blue). 
}
\label{fig:two_parameter_model_2D}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.45\textwidth]{paper/plots/pl18_taugtz_pc_zmax30_pl18_srollv2_with_and_without_physicality_prior.pdf}
\caption{Cumulative optical depth distributions from PC chains for zmax = 30 Planck 2018 srollv2 likelihood, with vs without physicality prior. 
}
\label{fig:plot_taugtz_2015_vs_2018_simallEE_vs_2018_srollv2}
\end{figure}

>>>>

\begin{figure}[t]
%\includegraphics[width=0.47\textwidth]{results/cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri.png}
\includegraphics[width=0.47\textwidth]{paper/plots/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri.pdf}
\caption{[Need to figure out dashed vs solid line convention in plots]. Marginalized posteriors for $\tauhi$ and $\taulo$ in the two-step model described in \refssec{example2}: effective reionization likelihood with f = 0.14 (red) agrees very well with the full likelihood results (blue). 
}
\label{fig:two_parameter_model_2D}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.5\textwidth]{paper/plots/pl18_taugtz_pc_zmax30_pl18_srollv2_with_and_without_physicality_prior.pdf}
\caption{Cumulative optical depth distributions from PC chains for zmax = 30 Planck 2018 srollv2 likelihood, with vs without physicality prior. 
}
\label{fig:plot_taugtz_2015_vs_2018_simallEE_vs_2018_srollv2}
\end{figure}
